\documentclass[10pt, letterpaper, tikz]{article}
\usepackage[utf8]{inputenc}
%\usepackage[T1]{fontenc}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=cyan,
}
\usepackage{listings}

% Directory Structures Configurations
\usepackage[edges]{forest}
\definecolor{foldercolor}{RGB}{124,166,198}

\tikzset{pics/folder/.style={code={%
    \node[inner sep=0pt, minimum size=#1](-foldericon){};
    \node[folder style, inner sep=0pt, minimum width=0.3*#1, minimum height=0.6*#1, above right, xshift=0.05*#1] at (-foldericon.west){};
    \node[folder style, inner sep=0pt, minimum size=#1] at (-foldericon.center){};}
    },
    pics/folder/.default={20pt},
    folder style/.style={draw=foldercolor!80!black,top color=foldercolor!40,bottom color=foldercolor}
}

\forestset{is file/.style={edge path'/.expanded={%
        ([xshift=\forestregister{folder indent}]!u.parent anchor) |- (.child anchor)},
        inner sep=1pt},
    this folder size/.style={edge path'/.expanded={%
        ([xshift=\forestregister{folder indent}]!u.parent anchor) |- (.child anchor) pic[solid]{folder=#1}}, inner xsep=0.6*#1},
    folder tree indent/.style={before computing xy={l=#1}},
    folder icons/.style={folder, this folder size=#1, folder tree indent=3*#1},
    folder icons/.default={12pt},
}

% URL Styling
\urlstyle{same}

\title{Chimera Embedded Driver Architecture}
\author{Brandon Braun}
\date{\today}

\begin{document}
  \begin{titlepage}
    \maketitle
  \end{titlepage}

\pagebreak
\tableofcontents

% ABSTRACT
  \pagebreak
  \begin{abstract}
    The Chimera Embedded System Driver architecture is split into high level and low level drivers to facilitate
    abstraction of hardware level MCU peripherals into a common framework. This eases development of new
    peripheral interfaces and provides a unified layout for projects to build on. This document summarizes the
    structure of the drivers and various thoughts behind its design.
  \end{abstract}

% INTRODUCTION
  \section{Introduction}
    The goal of Chimera is to provide a standard C++ API upon which I could build all my future embedded projects upon.
    While Linux exists and is a very useful and widely accepted approach to hardware driver development, it didn't
    offer any opportunity for personal growth in software architectural design. While a labor of love, Chimera is
    slowly improving into a useful tool for accessing common embedded peripherals in a manner that takes into account
    modern C++ concepts. The idea is that this approach will drive faster development of future projects by simplifying
    the requirements to get hardware up and running, while also offering more complex and modern functionality.

    From a conceptual perspective, Chimera provides an architectural specification that outlines how drivers for custom
    CPU/MCUs should be created, which is split into a high level driver(HLD) and low level driver (LLD). The HLD is
    platform agnostic and is responsible for the 'expected-use' functionality of a particular peripheral. Typically this involves generic
    configuration settings, reading and writing data, handling event callbacks, etc. The LLD is platform specific and is
    responsible for implementing hardware configuration aspects of the peripheral. It translates the generic HLD peripheral
    settings into the proper bits, bytes, and words that enable the desired functionality in the hardware. By following these
    specs, software built on top of it can be easily ported to other devices without much hassle. Simply swap out the low level
    driver and a new device is ready to go.

    For reference, this document outlines the \href{https://github.com/brandonbraun653/Thor}{Thor} driver implementation for
    Chimera, which adds STM32 device support. While some of the implementation details in the Thor LLD might not be portable to other
    devices, it serves as a good example of the kind of detail that might be needed to implement Chimera on another device.

% HIGH LEVEL DRIVER
  \pagebreak
  \section{Thor High Level Driver (HLD)}

  % INTRODUCTION
  \subsection{Introduction}
    The Thor high level driver handles commonly desired abstractions for various peripheral interfaces to help
    ease the integration of hardware peripherals into application code. The high level driver conforms to the
    Chimera interface specification through the use of pure virtual inheritance to ensure that applications can
    safely build on top of a Chimera driver implementation without worrying about the hardware details.


  % GENERIC STRUCTURE
  \subsection{Generic Structure}
    Each peripheral driver follows a particular structure to provide a consistent layout of the driver software.
    By keeping the folder/file structure consistent, it is expected to allow easier navigation of other peripheral
    drivers in the system. The current structure is outlined below and in later sections is described in detail:
  \paragraph{}
  \begin{forest}
    for tree={font=\sffamily, grow'=0,
    folder indent=.1em, folder icons,
    edge=densely dotted}
    [HLD Peripheral Driver (GPIO Example)
      [test
          [test\_entry\_gpio.cpp, is file]
          [test\_fixture\_gpio.cpp, is file]
          [test\_fixture\_gpio.hpp, is file]
          [test\_hld\_gpio\_chimera.cpp, is file]
          [test\_hld\_gpio\_driver.cpp, is file]
          ]
      [build.jam, is file]
      [hld\_gpio\_chimera.cpp, is file]
      [hld\_gpio\_chimera.hpp, is file]
      [hld\_gpio\_driver.cpp, is file]
      [hld\_gpio\_driver.hpp, is file]
      [hld\_gpio\_types.cpp, is file]
    ]
  \end{forest}

  \paragraph{hld\_$<$\emph{peripheral}$>$\_chimera.hpp:}\mbox{}\\
    Publicly declares the driver's interface to Chimera. It is expected that this will only be used internally
    within the driver implementation, but it may be useful to include this elsewhere.

  \paragraph{hld\_$<$\emph{peripheral}$>$\_chimera.cpp:}\mbox{}\\
    Implements the driver registration functionality to Chimera. Typically this involves definitions
    of the function prototypes in the associated driver interface header file and a function(s)
    that register the driver with the Chimera back end. If no driver is currently implemented for the
    given peripheral, then default behavior can be provided here.

  \paragraph{hld\_$<$\emph{peripheral}$>$\_driver.(c,h)pp:}\mbox{}\\
    These two files define the full HLD interface that can be used by projects. At a bare minimum, a
    peripheral driver class is declared that inherits from the Chimera virtual base class for that
    peripheral. This will guarantee the proper interface spec is upheld. Additional functionality can
    be declared that is not defined in Chimera, but it will not be propagated to Chimera peripheral
    objects.

  \paragraph{hld\_$<$\emph{peripheral}$>$\_types.hpp:}\mbox{}\\
    Defines commonly used types that are shared across all driver specific implementations. There is
    not likely to be much in this file as it's common for the Chimera driver defintions to be sufficient.

  % BUILD SYSTEM
  \subsection{Build System}


  % CHIMERA HOOKS
  \subsection{Chimera Hooks}




  % DRIVER IMPLEMENTATION
  \subsection{Driver Implementation}



  % Mention something about include headers

  % TEST IMPLEMENTATION
  \subsection{Test Implementation}




% LOW LEVEL DRIVER
  \pagebreak
  \section{Thor Low Level Driver (LLD)}
  \subsection{Introduction}

  \subsection{Interface Layer}



  \subsection{Driver Layer}

  \subsubsection{Generic Structure}

  \subsubsection{Build System}

  \subsubsection{Driver Implementation}

  \begin{lstlisting}

  \end{lstlisting}

\end{document}